rethinking antibiotics

### 2021-03-12 scripts/53_bayesian_5fam.Rmd
update

dat_cr <- dat %>% 
  filter(cr_d100 %in% c('yes','no')) %>% 
  mutate(cr_d100 = factor(cr_d100, levels = c('no','yes')))
```

>>>>

dat_cr <- dat %>% 
  filter(cr_d100 %in% c('yes','no')) %>% 
  mutate(cr_d100 = factor(cr_d100, levels = c('no','yes')))

# write out the sample and the log 10 genera 
dat %>% 
  select(sampleid, Akkermansia:Ruminococcus) %>% 
  write_csv('../data/amplicon/stool/combined_5_genera.csv')
```

### 2021-03-12 scripts/55_rethinking_abx.Rmd
update

---
title: "rethinking antibiotics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv') %>% 
  left_join(m)
```

>>>>

---
title: "rethinking antibiotics"
author: "Anqi Dai"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

@@

meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv') %>% 
  left_join(m) %>% 
  mutate(anaerobe_targeting = if_else(is.na(anaerobe_targeting), 'no', anaerobe_targeting)) %>% 
  mutate(anaerobe = if_else(anaerobe_targeting == 'no', 1, 2))

set.seed(123)
dat_list <- list(
    tox = meta$tox,
    cr100 = meta$cr100,
    location = meta$loca,
    anaerobe = meta$anaerobe
    )

meta %>% 
  count(center, anaerobe_targeting) 
```

```{r}   
atox <- ulam(
    alist(
        tox ~ dbinom( 1 , p ) ,
        logit(p) <- b[anaerobe] + a[location] ,
        b[anaerobe] ~ dnorm( 0 , 1), 
        a[location] ~ dnorm( 0 , 0.5 )
    ) , data=dat_list , chains=4 , log_lik=TRUE , cores = 8)
precis(atox, depth = 2)
plot(precis(atox, depth = 2) ) 
# seems anaerobe abx is positively linked with toxicity 
```

## CR day 100

```{r}
acr <- ulam(  
    alist(
        cr100 ~ dbinom( 1 , p ) ,
        logit(p) <- b[anaerobe] + a[location] ,
        b[anaerobe] ~ dnorm( 0 , 1), 
        a[location] ~ dnorm( 0 , 0.5 )
    ) , data=dat_list , chains=4 , log_lik=TRUE , cores = 8)
precis(acr, depth = 2)
plot(precis(acr, depth = 2) ) 
# nothing interesting 
```
